Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-19 paper/paper.tex
Add paper inside the related work section

Lamkanfi et. al \cite{lamkanfi2010predicting} show a method through which one
can predict the severity of a reported bug (i.e. assign story points to the 
ticket) automatically. The authors conducted their research on the Mozilla,
Eclipse and GNOME projects and divided their method into four steps:
  \begin{itemize}
    \item extract and organize bug reports;
    \item pre-process bug reports - tokenization, stop word removal and stemming;
    \item train the classifier on multiple datasets of bug reports - 70\% 
      training and 30\% evaluation;
    \item apply the trained classifier on the evaluation set.
  \end{itemize}
The conclusions they drew from running the evaluation process were rather 
interesting:
  \begin{itemize}
    \item terms such as deadlock, hand, crash, memory or segfault usually indicate
      a severe bug; however, there are other terms that can indicate the opposite,
      such as typos;
    \item when analyzing the textual description they found that using simple
      one line summaries resulted in less false positives and increased precision
      levels;
    \item the classifier needs a large dataset in order to predict correctly;
    \item depending on how well a software project is componentized, one can 
      use a predictor per component rather than an universal one.
  \end{itemize}

>>>>

Having discussed about various factors that can influence the quality in software tickets, 
we also need to take into account how can we apply this knowledge to solving the issue of 
poor design in issue tracking systems and how the ticket creation process could be improved. 
The study conducted by Lamkanfi et. al \cite{lamkanfi2010predicting} looks at this aspect and
shows how issue tracking systems could be extended in order to automatically generate the severity 
of a ticket (e.g. assign story points to a Jira issue). The authors conducted their research on the Mozilla,
GNOME and Eclipse and projects and split their approach into four steps:
  \begin{itemize}
    \item extract and organize tickets;
    \item pre-process tickets (i.e. tokenization, stop word removal and stemming);
    \item train the classifier on two datasets of tickets - 70\% 
      training and 30\% evaluation;
    \item apply the trained classifier on the evaluation set.
  \end{itemize}
The conclusions they drew from running the evaluation process were rather 
interesting:
  \begin{itemize}
    \item terms such as segfault, deadlock, crash, hand or memory typically indicate
      a severe bug;
    \item when analyzing the textual description they found that using simple
      one line summaries resulted in less false positives and increased precision
      levels;
    \item the classifier needs a large number of tickets in order to predict correctly;
    \item depending on how well a software project is modularised, one can 
      use a predictor per module rather than a universal one.
  \end{itemize}
